---
pagetitle: "KDSC | ARISE Data Log"
toc: false
css: datalog_style.css
---

## What's in this page? {.main-header}

In this page, you can see the data log for the [ARISE](https://nsfepscor.ku.edu/track-1-arise) projects. Adaptive and Resilient Infrastructures Driven by Social Equity (ARISE) is a NSF EPSCoR initiative that helps Kansas communities rebound faster from large-scale disasters. The project unites over 70 researchers across 18 partner institutions to build research capacity and develop new decision-support tools for managing human and physical infrastructure. As a part of ARISE team, we share data log for the ARISE projects which includes KDSC projects. If you are interested in getting access to level 2 or level 3 data, please contact xxx.

```{r}
#| echo: false
#| output: false
#| warning: false

library(readxl)
library(tidyverse)
library(DT)

kdsc_data <- read_excel("C:/Users/d497j944/Downloads/KDSC Data Log.xlsx") |> 
  select(1:3)
```

## Data Log {.main-header}
```{r}
#| echo: false

kdsc_data |> 
  DT::datatable(
    options = list(columnDefs = list(list(className = 'dt-center', targets = '_all')))
  )
```
