---
dataset-title: "Kansas Child Care Facility Data (2017-2024)"
toc: false
---

```{=html}
<link rel="stylesheet" href="../../project_dataset_style.css">

<div class="dataset-container">
    <!-- Header Section -->
    <header class="dataset-header">
        <p class="header-tagline">Project Dataset</p>
        <h2 class="header-title"> {{< meta dataset-title >}}</h2>
        <div class="header-buttons">
            <a href="https://github.com/KansasData/CommunityDataLab/raw/main/Kansas%20Action%20for%20Children/kac_data.zip" class="btn btn-download" download="kac_data.zip">
                <i class="bi bi-file-earmark-zip-fill icon"></i> Download Full Dataset (.zip)
            </a>
            
            <a href="../projects/project_KAC.html" class="btn btn-project">
                <i class="bi bi-info-circle-fill icon"></i> View Project Page
            </a>
            
            <a href="../classplan/class_KAC.html" class="btn btn-classplan">
                <i class="bi bi-book-half icon"></i> View the Class Plan
            </a> 
            
        </div>
    </header>
</div>
```

:::::: content-card
## About the Data

This project utilizes a variety of datasets to assess the child care climate in Kansas. Key data sources include Kansas child care licensing information from the KIDS COUNT Data Center and accessibility data from Child Care Aware of Kansas. The compiled dataset provides a comprehensive landscape of child care in Kansas from 2017 to 2024.

It includes two primary files: one detailing the annual trends in facility types and total capacity statewide, and another providing a county-level breakdown of different care facilities for 2024. The data has been cleaned and refined from original PDF reports to be analysis-ready.

## Data Dictionary

```{r}
#| echo: false
#| message: false
#| include: false
library(tidyverse)
library(DT)
```

::: panel-tabset
### Kansas Trend (2017 - 2024)

```{r}
#| echo: false
#| message: false
kac_data <- read_csv("https://raw.githubusercontent.com/KansasData/CommunityDataLab/refs/heads/main/Kansas%20Action%20for%20Children/care_facility.csv")

dic_kac <- tibble(
  `Variable Name` = c("Program Type", "Total Facilities", "Total Capacity", "year"),
  `Description` = c("Name of child care program type", "Total Number of Facilities providing a corresponding program", "Total number of child care capcaity", "The year the data was reported"),
  `Data Type` = c("String", "Integer", "Integer", "Integer")
) 

dic_kac |> datatable()
```

### County Level Lanscape (2024)

```{r}
#| echo: false
#| message: false
county_facility <- read_csv("https://raw.githubusercontent.com/KansasData/CommunityDataLab/refs/heads/main/Kansas%20Action%20for%20Children/county_facility.csv")
county_facility |> 
  datatable()

dic_county <- tibble(
  `Varaible Name` = c("county", "care_facility", "n_child_enrolled", "n_desired_cap", "nlicensed_cap", "n_dcf", "n_food_program"),
  `Description` = c("The name of the Kansas county", "The type of child care center", "The number of children currently enrolled at the facility", "The total desired capacity for the facility type in that county", "The total licensed capacity for the facility type in that county", "The total number of facility providing DCF program", "The total number of facility providing food program")
)

dic_county |> datatable()

```
:::

## Quick Start Guide

::: panel-tabset
### Python

```{python}
#| eval: false
import pandas as pd

# URL to the raw CSV file  on GitHub
url_county = 'https://raw.githubusercontent.com/KansasData/CommunityDataLab/refs/heads/main/Kansas%20Action%20for%20Children/county_facility.csv'

url_ks = 'https://raw.githubusercontent.com/KansasData/CommunityDataLab/refs/heads/main/Kansas%20Action%20for%20Children/care_facility.csv'

# Read the data
df_county = pd.read_csv(url_county)

df_ks = pd.read_csv(url_ks)

# Display the first 5 rows
print(df_county.head())
print(df_ks.head())

```

### R

```{r}
#| eval: false
# Install and load the readr library if you haven't already
# install.packages("readr")
library(readr)

# URL to the raw CSV file on GitHub
url_county <- 'https://raw.githubusercontent.com/KansasData/CommunityDataLab/refs/heads/main/Kansas%20Action%20for%20Children/county_facility.csv'

url_ks <- 'https://raw.githubusercontent.com/KansasData/CommunityDataLab/refs/heads/main/Kansas%20Action%20for%20Children/care_facility.csv'

# Read the data
df_county <- read_csv(url_county)

df_ks = read_csv(url_ks)

# Display the first 6 rows
print(head(df_county))
print(head(df_ks))
```
:::

## Data Preview

::: panel-tabset
### Kansas care facility trend data from 2017 to 2023

```{r}
#| echo: false
#| message: false

# Read the first few rows of the CSV file
kac_data_preview <- read_csv("https://raw.githubusercontent.com/KansasData/CommunityDataLab/refs/heads/main/Kansas%20Action%20for%20Children/care_facility.csv")

# Display the data preview
kac_data_preview |> 
  datatable()
```

### Child care facility landscape for Kansas county

```{r}
#| echo: false
#| message: false

county_facility <- read_csv("https://raw.githubusercontent.com/KansasData/CommunityDataLab/refs/heads/main/Kansas%20Action%20for%20Children/county_facility.csv")
county_facility |> 
  datatable()
```
:::
::::::
