---
title: "Kansas Action for Children"
categories:
  - Child Care
date: "2024-05-01"
date-format: "YYYY"
author: "Community Provided"

---

## Download the Dataset

You can download the dataset using the link below:

[Download Dataset](Kansas%20Action%20For%20Children.zip)

## Data Description

The project utilizes a variety of datasets to assess the child care climate in Kansas state. Key data sources include Kansas child care licensing information from the KIDS COUNT Data Center, accessibility data from Child Care Aware of Kansas. This dataset provides a comprehensive landscape of the child care in Kansas from 2017 to 2024. It includes data on various types of child care facilities, including child care centers and licensed family/group homes, as well as their capacities and enrollment figures.

The data includes original data source (i.e., PDF file) from the Child Care Aware of Kansas report as well as refined dataset used in the analysis.

## Data Preview

### Kansas care facility trend data from 2017 to 2023

```{r}
#| echo: false
#| message: false

library(tidyverse)
library(DT)

# Read the first few rows of the CSV file
kac_data_preview <- read_rds("./Data/cleaned_ks/care_facility.rds")

# Display the data preview
kac_data_preview |> 
  datatable()
```

### Child care facility landscape for Kansas county

```{r}
#| echo: false
#| message: false

county_facility <- read_rds("./Data/cleaned_ks/county_facility.rds")
county_facility |> 
  datatable()
```
